---
title: "Activity 1.2 - RStudio and R Markdown"
author: "anisha"
date: "8/26/2019"
output: 
  html_document: 
    fig_height: 9
    fig_width: 15
    highlight: pygments
    theme: united
    toc_depth: 4
---

### Load packages

```{r load-packages, message=FALSE}

library(tidyverse) 
library(datasauRus)
```
datasaurus_dozen %>%
count(dataset) %>%
print(13)

### Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code.)
## 1846 rows and 3 variables are there ## 
## dataset, x, y are the variables included in the data frames ##


### Exercise 2

##First let's plot the data in the dino dataset:

 ```{r plot-dino, fig.height=3, fig.width=6}
 
  dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
  ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
  
```
  
#And next calculate the correlation between x and y in this dataset:
### summarizes helps to get the summary of the data###

```{r cor-dino}

dino_data %>%
summarize(r = cor(x, y))

```

### Exercise 3

 ```{r plot-star, fig.height=3, fig.width=6}
 
  star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
  ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
  
```

```{r cor-star}

star_data %>%
summarize(r = cor(x, y))

```

### Exercise 4

```{r plot-circle, fig.height=3, fig.width=6}
 
  circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
  ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
  
```

```{r cor-circle}

circle_data %>%
summarize(r = cor(x, y))

```
### There is not much difference between in corelation between dino and circle ###


### Exercise 5
### ggplot helps to declare the input data frame for a graphic and to specify the set of plot ###

```{r}
ggplot(data = datasaurus_dozen, aes(x=x, y=y, color = dataset)) + geom_point() + facet_wrap(~dataset, ncol=3) + theme(legend.position = "none")

```


```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r=cor(x,y)) %>%
print(13)

```




